Performance of two different ontological and data access methods

### 2014-07-08 cold2014/magnus.tex
explain ontology approach
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@742 43ef1190-90fd-4dd7-a769-d0121f02b80e

\subsection{Running the experiments}
In this section we will present several experiments with different
number of factors.  The objective is to find out how the ontologies
will perform in comparison and identifying which factors affect the
outcome of each experiment. We did the ontology alignment and
development of the application to prevent the loss of precision with
either ontology.

>>>>

\subsection{Running the experiments}
In this section we will present several experiments with different
number of factors.  The objective is to find out how the two approaches
will perform in comparison and identifying which factors affect the
outcome of each experiment. Although the ontology is not the
only issue that distinguishes these approaches, it is the key feature,
and therefore, we will shall refer to that as a factor.
